Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-02 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Edits to draft

Good Characteristics:
- Measureable at the county/sub-county level
- Internally consistant (either within a study or for a particular storm)
+ Takes into account the unique characteristics of a particular storm and county's location in assessing exposure
- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:
- Distance alone
- Wind alone
- Metrics that cannot be widely measured at the county or sub-county level (i.e., stress)

@@

Our analysis included [x] Atlantic basin tropical storms over the years 1988 to 2011. This dataset includes several noteworthy storms, including Hugo (1989), Andrew (1992), Floyd (1999), Katrina (2005), ... .

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Map of tracks of all storms in study.
data("closest_dist")
storms <- unique(closest_dist$storm_id)
storms <- storms[which(gsub("*.+-", "", storms) <= 2011)]
map_tracks(storms, plot_points = FALSE, alpha = 0.3)
```

@@

Justification of NLDAS data: comparison of NLDAS and gauge data for hurricane Alex (2010).

```{r echo = FALSE, fig.height = 4, fig.width = 6}
#library(data.table)
#alex_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_Alex_Rain.csv", header = TRUE)
#save(alex_gauge, file = "writing/DraftExposurePaper/alex_gauge.RData")
# load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/alex_gauge.Rdata")
load("alex_gauge.Rdata")
alex_nldas <- county_rain(counties = unique(alex_gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
alex_nldas <- alex_nldas %>%
        filter(storm_id == "Alex-2010")
alex_gauge$fips <- as.character(alex_gauge$fips)
compare_rain <- right_join(alex_nldas, alex_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)")  + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

```{r echo = FALSE, fig.height = 4, fig.width = 6}
#allison_gauge <- read.csv("~/Documents/hurricaneexposure/writing/DraftExposurePaper/MWR_gauge_rain_data/allison_mwr.csv")
allison_gauge <- read.csv("MWR_gauge_rain_data/allison_mwr.csv")
allison_nldas <- county_rain(counties = unique(allison_gauge$fips),
                             start_year = 2001, end_year = 2001,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
allison_nldas <- allison_nldas %>%
        filter(storm_id == "Allison-2001")
allison_gauge$fips <- as.character(allison_gauge$fips)
compare_rain <- right_join(allison_nldas, allison_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(25, 200)) + ylim(c(25, 800)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
load("ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain <- right_join(ike_nldas, ike_gauge, by = "fips")
#ike_nldas <- as.data.table(alex_nldas)
#ike_gauge <- as.data.table(alex_gauge)
#compare_rain1 <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

[JMF-- Missing values are those from Arkansas (missing the leading 0 in fips code)]

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```

@@

```{r}
#frances_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_gauge.csv", header = TRUE)
#save(frances_gauge, file = "writing/DraftExposurePaper/frances_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/frances_gauge.RData")
load("frances_gauge.RData")
frances_gauge$precip_mm <- convert_precip(frances_gauge$precip_in, "inches", "mm")
frances_nldas <- county_rain(counties = unique(frances_gauge$fips),
                             start_year = 2004, end_year = 2004,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
frances_nldas <- frances_nldas %>%
        filter(storm_id == "Frances-2004")
frances_gauge$fips <- as.character(frances_gauge$fips)
compare_rain <- right_join(frances_nldas, frances_gauge, by = "fips")
b <- ggplot(compare_rain, aes(x = tot_precip, y = precip_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

@@

```{r}
#Ike-2008 wind
#ike_wind <- read.csv("/Users/joshuaferreri/Documents/ike_wind.csv", na.strings = 999, header = TRUE)
#save(ike_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
# load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_wind.RData")
load("ike_wind.RData")
```

@@

```{r eval = FALSE}
#frances_wind <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_wind.csv", 
 #                        na.strings = 999,
  #                       header = TRUE)
#save(frances_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
```

```{r}
load("frances_wind.RData")
```

@@

```{r eval = FALSE}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
```
```{r}
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
```
```{r}
#Allison-2010
allison_fips <- allison_nldas$fips
allison_fips <- unique(allison_fips)
```
```{r}
#Frances-2004
frances_fips <- frances_nldas$fips
frances_fips <- unique(frances_fips)
```

>>>>

Good Characteristics:

- Flooding-- Most associated with death; property damage
- Precipitation
- Wind (potentially weighted)

Bad Characteristics:

- Distance alone
- Wind alone
- Not consistent across storms. (For example, if a metric classified a county as "exposed" to a storm late in the dataset, if the same storm had happened earlier in the dataset, it also would have been assessed as "exposed". This might be the case for, for example, NOAA Storm Events. It might be more common to report an event well enough that it makes it into the database in later years compared to earlier years of the study.)
- Not consistent across locations for a single storm. (For example, some of the metrics depend on subjective judgement of different people in different locations-- I think FEMA disaster declarations and NOAA Storm Events might both be examples in this. In this case, you couldn't rely on the assumption that, if two counties have the same level of exposure to a storm, they would have the same status on that criterion.)

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Vector of all storms in study.
data("closest_dist")
storms <- unique(closest_dist$storm_id)
storms <- storms[which(gsub("*.+-", "", storms) <= 2011)]
```

Our analysis included `r length(storms)` Atlantic basin tropical storms over the years 1988 to 2011. This dataset includes several noteworthy storms, including Hugo (1989), Andrew (1992), Floyd (1999), Katrina (2005), [maybe add Ike, Ivan, others?] ... .

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Map of tracks of all storms in study.
map_tracks(storms, plot_points = FALSE, alpha = 0.3)
```

@@

We compared exposure results based on the NLDAS-2 precipitation data with values from monitors reported for certain storms in the *Monthly Weather Reviews* yearly summary of the Atlantic basin tropical storm season. Here are some of the plots comparing county-level estimates of rain exposure from the NLDAS-2 data to all *MWR*-reported rainfall estimates within the county:

```{r echo = FALSE, fig.height = 4, fig.width = 6}
load("alex_gauge.Rdata")
alex_nldas <- county_rain(counties = unique(alex_gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
alex_nldas <- alex_nldas %>%
        filter(storm_id == "Alex-2010")
alex_gauge$fips <- as.character(alex_gauge$fips)
compare_rain <- right_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Alex, 2010")
a

county_range <- compare_rain %>% 
        group_by(fips) %>%
        summarize(lowest_rain = min(rain_mm),
                  highest_rain = max(rain_mm),
                  nldas_rain = mean(tot_precip))
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm)) + 
        geom_segment(data = county_range, 
                     aes(x = nldas_rain, xend = nldas_rain,
                         y = lowest_rain, yend = highest_rain,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_rain$tot_precip, compare_rain$rain_mm)) +
        ylim(range(compare_rain$tot_precip, compare_rain$rain_mm)) + 
        ggtitle("Alex, 2010") + 
        xlab("NLDAS-2 rainfall (mm)") + 
        ylab("MWR rainfall reports (mm)")
b
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)")  + 
        ggtitle("Alex, 2010") + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

```{r echo = FALSE, fig.height = 4, fig.width = 6}
allison_gauge <- read.csv("MWR_gauge_rain_data/allison_mwr.csv")
allison_nldas <- county_rain(counties = unique(allison_gauge$fips),
                             start_year = 2001, end_year = 2001,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
allison_nldas <- allison_nldas %>%
        filter(storm_id == "Allison-2001")
allison_gauge$fips <- as.character(allison_gauge$fips)
compare_rain <- right_join(allison_nldas, allison_gauge, by = "fips")

a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Allison, 2011")
a
county_range <- compare_rain %>% 
        group_by(fips) %>%
        summarize(lowest_rain = min(rain_mm),
                  highest_rain = max(rain_mm),
                  nldas_rain = mean(tot_precip))
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm)) + 
        geom_segment(data = county_range, 
                     aes(x = nldas_rain, xend = nldas_rain,
                         y = lowest_rain, yend = highest_rain,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_rain$tot_precip, compare_rain$rain_mm)) +
        ylim(range(compare_rain$tot_precip, compare_rain$rain_mm)) + 
        ggtitle("Allison, 2001") + 
        xlab("NLDAS-2 rainfall (mm)") + 
        ylab("MWR rainfall reports (mm)")
b
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(25, 200)) + ylim(c(25, 800)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        ggtitle("Allison, 2001") + 
        scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "black"), 
                           guide = "none") 
```

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
load("ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_gauge$fips <- sprintf("%05s", ike_gauge$fips)
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain <- right_join(ike_nldas, ike_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Ike, 2008")
a

county_range <- compare_rain %>% 
        group_by(fips) %>%
        summarize(lowest_rain = min(rain_mm),
                  highest_rain = max(rain_mm),
                  nldas_rain = mean(tot_precip))
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm)) + 
        geom_segment(data = county_range, 
                     aes(x = nldas_rain, xend = nldas_rain,
                         y = lowest_rain, yend = highest_rain,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_rain$tot_precip, compare_rain$rain_mm)) +
        ylim(range(compare_rain$tot_precip, compare_rain$rain_mm)) + 
        ggtitle("Ike, 2008") + 
        xlab("NLDAS-2 rainfall (mm)") + 
        ylab("MWR rainfall reports (mm)")
b
```

[JMF-- Missing values are those from Arkansas (missing the leading 0 in fips code); GBA: I fixed this. This is ultimately something I need to fix in the `hurricaneexposure` package, but I've got this example fixed to run without losing the FIPS with leading zeros.]

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        ggtitle("Allison, 2001") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```

@@

```{r}
load("frances_gauge.RData")
frances_gauge$rain_mm <- convert_precip(frances_gauge$precip_in, "inches", "mm")
frances_gauge$fips <- sprintf("%05s", frances_gauge$fips)
frances_nldas <- county_rain(counties = unique(frances_gauge$fips),
                             start_year = 2004, end_year = 2004,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
frances_nldas <- frances_nldas %>%
        filter(storm_id == "Frances-2004")
frances_gauge$fips <- as.character(frances_gauge$fips)
compare_rain <- right_join(frances_nldas, frances_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Frances, 2004")
a

county_range <- compare_rain %>% 
        group_by(fips) %>%
        summarize(lowest_rain = min(rain_mm),
                  highest_rain = max(rain_mm),
                  nldas_rain = mean(tot_precip))
b <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm)) + 
        geom_segment(data = county_range, 
                     aes(x = nldas_rain, xend = nldas_rain,
                         y = lowest_rain, yend = highest_rain,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_rain$tot_precip, compare_rain$rain_mm)) +
        ylim(range(compare_rain$tot_precip, compare_rain$rain_mm)) + 
        ggtitle("Frances, 2004") + 
        xlab("NLDAS-2 rainfall (mm)") + 
        ylab("MWR rainfall reports (mm)")
b
```

@@

```{r}
#Ike-2008 wind
load("ike_wind.RData")
ike_wind <- ike_wind %>%
        filter(!is.na(max_sust_kt)) %>%
        mutate(max_sust_mps = convert_wind_speed(max_sust_kt, 
                                                 old_metric = "knots",
                                                 new_metric = "mps"),
               fips = sprintf("%05s", fips))

ike_wind_model <- county_wind(counties = unique(ike_wind$fips),
                              start_year = 2008, end_year = 2008,
                              wind_limit = 0) %>%
        filter(storm_id == "Ike-2008")

compare_wind <- right_join(ike_wind_model, ike_wind, by = "fips")
a <- ggplot(compare_wind, aes(x = max_sust, y = max_sust_mps,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Ike, 2008")
a

county_range <- compare_wind %>% 
        group_by(fips) %>%
        summarize(lowest_wind = min(max_sust_mps),
                  highest_wind = max(max_sust_mps),
                  model_wind = mean(max_sust))
b <- ggplot(compare_wind, aes(x = max_sust, y = max_sust_mps)) + 
        geom_segment(data = county_range, 
                     aes(x = model_wind, xend = model_wind,
                         y = lowest_wind, yend = highest_wind,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_wind$max_sust, compare_wind$max_sust_mps)) +
        ylim(range(compare_wind$max_sust, compare_wind$max_sust_mps)) + 
        ggtitle("Ike, 2008") + 
        xlab("Modeled wind speed (m / s)") + 
        ylab("MWR wind reports (m / s)")
b
```

@@

```{r eval = FALSE}
frances_wind <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_wind.csv", 
                         na.strings = 999,
                         header = TRUE)
save(frances_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
```

```{r}
load("frances_wind.RData")
frances_wind <- frances_wind %>%
        filter(!is.na(max_sust_kt)) %>%
        mutate(max_sust_mps = convert_wind_speed(max_sust_kt, 
                                                 old_metric = "knots",
                                                 new_metric = "mps"),
               fips = sprintf("%05s", fips))

frances_wind_model <- county_wind(counties = unique(frances_wind$fips),
                              start_year = 2004, end_year = 2004,
                              wind_limit = 0) %>%
        filter(storm_id == "Frances-2004")

compare_wind <- right_join(frances_wind_model, frances_wind, by = "fips")
a <- ggplot(compare_wind, aes(x = max_sust, y = max_sust_mps,
                              color = fips)) +
        geom_point() + 
        theme_bw() + 
        ggtitle("Frances, 2004")
a

county_range <- compare_wind %>% 
        group_by(fips) %>%
        summarize(lowest_wind = min(max_sust_mps),
                  highest_wind = max(max_sust_mps),
                  model_wind = mean(max_sust))
b <- ggplot(compare_wind, aes(x = max_sust, y = max_sust_mps)) + 
        geom_segment(data = county_range, 
                     aes(x = model_wind, xend = model_wind,
                         y = lowest_wind, yend = highest_wind,
                         group = fips), color = "gray") + 
        geom_point(aes(group = NA), alpha = 0.5) + 
        ggthemes::theme_few() + 
        geom_abline(aes(intercept = 0, slope = 1)) + 
        xlim(range(compare_wind$max_sust, compare_wind$max_sust_mps)) +
        ylim(range(compare_wind$max_sust, compare_wind$max_sust_mps)) + 
        ggtitle("Frances, 2004") + 
        xlab("Modeled wind speed (m / s)") + 
        ylab("MWR wind reports (m / s)")
b
```

@@

```{r eval = FALSE}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
```
```{r}
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
```
